Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.0

### 2019-06-05 manuscript.Rmd
fixed fig 1 legend issue

core_both  %>% mutate(Tissue = case_when(study_accession == 'SRP012682' ~ 'GTEx', TRUE ~ Tissue),
                      Sub_Tissue = case_when(study_accession == 'SRP012682' ~ 'GTEx', TRUE ~ Sub_Tissue),
                      Sub_Tissue = case_when(grepl('MGS', Sub_Tissue) ~ 'Retina - Adult AMD Tissue', TRUE ~ Sub_Tissue)) %>% 
  filter(grepl('GTEx|Retina|Cornea|Lens|RPE', Tissue)) %>% unique() %>% 
  #mutate(Sub_Tissue = case_when(sample_accession == 'SRS1955479' ~ 'Retina - Adult Tissue', TRUE ~ Sub_Tissue)) %>%
  group_by(Tissue, Sub_Tissue, Version) %>% summarise(Count=n()) %>% 
  mutate(Dataset = Version) %>% 
  ggplot(aes(x=Sub_Tissue, y= log2(Count), fill = Tissue, alpha = Dataset, label = Count, group = Dataset)) + 
  geom_bar(stat = 'identity', position = position_dodge(width = NULL)) + 
  theme_minimal() + 
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.3))  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  xlab('') + 
  geom_label_repel(stat = 'identity', position = position_dodge(width = 0.9), size = 4, ylim =c(3, NA)) + 
  ylab('log2(Count of Samples)') + scale_alpha_manual(values = c(0.5,1)) +
  #coord_cartesian(ylim = c(0,11)) +
  theme(text = element_text(size = 10)) +
  custom_fill

>>>>

core_both  %>% mutate(Tissue = case_when(study_accession == 'SRP012682' ~ 'GTEx', TRUE ~ Tissue),
                      Sub_Tissue = case_when(study_accession == 'SRP012682' ~ 'GTEx', TRUE ~ Sub_Tissue),
                      Sub_Tissue = case_when(grepl('MGS', Sub_Tissue) ~ 'Retina - Adult AMD Tissue', TRUE ~ Sub_Tissue)) %>% 
  filter(grepl('GTEx|Retina|Cornea|Lens|RPE', Tissue)) %>% unique() %>% 
  #mutate(Sub_Tissue = case_when(sample_accession == 'SRS1955479' ~ 'Retina - Adult Tissue', TRUE ~ Sub_Tissue)) %>%
  group_by(Tissue, Sub_Tissue, Version) %>% summarise(Count=n()) %>% 
  mutate(Dataset = Version) %>% 
  ggplot(aes(x=Sub_Tissue, y= log2(Count), fill = Tissue, alpha = Dataset, label = Count, group = Dataset)) + 
  geom_bar(stat = 'identity', position = position_dodge(width = NULL)) + 
  theme_minimal() + 
  theme(axis.text.x=element_text(angle=90, hjust=1, vjust=0.3))  + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
  xlab('') + 
  geom_label_repel(stat = 'identity', position = position_dodge(width = 0.9), size = 4, ylim =c(3, NA), show.legend = FALSEx) + 
  ylab('log2(Count of Samples)') + scale_alpha_manual(values = c(0.5,1)) +
  #coord_cartesian(ylim = c(0,11)) +
  theme(text = element_text(size = 10)) +
  custom_fill
